\chapter{About 3dengfx}

3dengfx is a realtime visualization system, commonly refered to as 3d engine,
that provides a framework to help you easily create 3d graphics programs.
3dengfx provides various abstraction layers presenting a very easy way to do most
useful tasks, and at the same time it is designed to be versatile enough to give
you the ability to bypass any of these abstractions in case they don't provide
the needed functionality. Furthermore, 3dengfx is very good as a building block
to create any functionality that you need on top of it; and the fact that it is
licensed under the terms of free software makes it possible to adapt it to fit
your needs.

\section{License}
The 3dengfx realtime visualization system is free software and is released under
the GNU General Public License version 2 (see COPYING in the root directory of
3dengfx, or view it online at \verb|http://www.fsf.org/licenses/gpl.html|).
In a few words and without legal terms, this means that you can use this library
for whatever purpose (including commercial purposes), you can modify it to fit
your needs, you can redistribute it modified or unmodified, with or without a
distribution fee, but anything that you release which contains or links against
this library with or without modifications must be released under the same
terms, no more and no less (i.e. under the GPL v2 or newer).

Note that the above is just a description based on my understanding of the GPL,
in case of contradiction, the actual text of the GPL is correct and in effect,
not this description.

\section{Authors}

Main developer:\\
John Tsiombikas \verb|<nuclear@siggraph.org>|\\
\\
Contributors:\\
Mihalis Georgoulopoulos \verb|<msamurai@freemail.gr>|

\section{How to get 3dengfx}

At the website of 3dengfx \verb|http://thelab.demoscene.gr/nuclear/3dengfx/|,
you can always find there the latest release of the library as well as news,
sample programs, etc.

Alternatively you may get the latest development version through anonymous svn
at \verb|svn://nuclead.dnsalias.com/pub/3dengfx|. This repository is on my
personal computer and while it should be accessible almost all the time, there
might be some periods of downtime, so if you cannot reach it, try again a little
later.

\section{How to contribute to 3dengfx}

If you want to contribute to the project, you can send patches in the form of
unified diffs (diff -u), against the latest development version. If you plan to
contribute a lot, and feel qualified to join the development team don't hesitate
to contact the main developer of the project through email.
